A Hybrid Ensemble Learning Approach to Star-galaxy Classification

### 2015-03-30 paper/main.tex
galaxy spectra are interpolated.

As the goal of template fitting methods is to minimize
the difference between observed and theoretical magnitudes,
this approach heavily relies on
both the use of SED templates and
the accuracy of the transmission functions
for the filters used for particular survey.
For our stellar templates,
we use the empirical SED library from \cite{pickles1998stellar}.
The Pickles library consists of 131 stellar templates,
which span all normal spectral types
and luminosity classes at solar abundance,
as well as metal-poor and metal-rich F-K dwarf 
and G-K giant and supergiant stars.
For our galaxy templates,
we use the four CWW spectra from \cite{coleman1980colors},
which include an Elliptical, an Sba, an Sbb,
and an Irregular galaxy template.
When extending an analysis to higher redshift,
the CWW library is often augmented with
two star bursting galaxy templates from \cite{kinney1996template}.
\textcolor{red}{interpolated}.

>>>>

As the goal of template fitting methods is to minimize
the difference between observed and theoretical magnitudes,
this approach heavily relies on
both the use of SED templates and
the accuracy of the transmission functions
for the filters used for particular survey.
For our stellar templates,
we use the empirical SED library from \cite{pickles1998stellar}.
The Pickles library consists of 131 stellar templates,
which span all normal spectral types
and luminosity classes at solar abundance,
as well as metal-poor and metal-rich F-K dwarf 
and G-K giant and supergiant stars.
\textcolor{blue}{
We supplement the stellar library with
100 SEDs from \cite{chabrier2000evolutionary},
which include low mass stars and brown dwarfs
with different $T_{eff}$ and surface gravities.
We also include four white dwarf templates of
\cite{bohlin1995white}.
}
For our galaxy templates,
we use the four CWW spectra from \cite{coleman1980colors},
which include an Elliptical, an Sba, an Sbb,
and an Irregular galaxy template.
When extending an analysis to higher redshift,
the CWW library is often augmented with
two star bursting galaxy templates from \cite{kinney1996template}.
\textcolor{blue}{
From the six original CWW and Kinney spectra,
intermediate templates are created by interpolation
for a total of 51 SEDs.
}
